An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-22 EconGrowth-R-Functions.Rnw
Working toward a second graph to be used as a doubleY to show diagonal lines on the triangle plots.

########################
# Creates a lattice plot that has the size of confidence intervals on the vertical axis and parameter
# values on the horizontal axis.
# At this point, this function is NOT a general-purpose function, as the number of permutations
# of model, parameter, energy type, and factor is too varied to be able to turn into a general-purpose 
# graph with little time investment at this point.
# This function makes a lattice plot with the following panels (in the arrangement shown)
#
# gammaCDeq   gammaCDex    gammaCDeu
# deltaCESeq  deltaCESex   deltaCESeu
# sigmaCESeq  sigmaCESex   sigmaCESeu
#
# Parameters and models (gamma for CDe and delta and sigma for CESe) are in rows and energyTypes (q, x, and u) 
# are in columns.
##
CIvsParamLattice <- function(descriptors){
  # Build a data.frame that has all the necessary models
  gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
  gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
  gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
  deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
  sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
  # Change the name of the first columns (the ones that contain the parameter of interest to us) to "param".
  # Doing this allows us to combine the individual data frames into one large data frame.
  colnames(gammaCDeqDF)[1]  <- "param"
  colnames(gammaCDexDF)[1]  <- "param"
  colnames(gammaCDeuDF)[1]  <- "param"
  colnames(deltaCESeqDF)[1] <- "param"
  colnames(deltaCESexDF)[1] <- "param"
  colnames(deltaCESeuDF)[1] <- "param"
  colnames(sigmaCESeqDF)[1] <- "param"
  colnames(sigmaCESexDF)[1] <- "param"
  colnames(sigmaCESeuDF)[1] <- "param"
  # Create one big data.frame with all of the data.
  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
  # Now make the graph.
  # Need to use the indices in the following code, because the column labels will be different for each type
  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
  # plot <-  xyplot(data$CI ~ data$sigma, ...)
  # would break if we, instead, wanted CESe with Q and plotting delta.
  # So, instead, we use the column indices to pick off the correct variables.
  # data[ , 1] contains the the parameter; 
  # data[ , 2] contains the CI width; 
  # data[ , 3] contains the descriptor for the type of graph it is.
  plot <- xyplot(data[ , 2] ~ data[ , 1] | data[ , 3], 
#                  xlab=list(label=xLabel),
#                  ylab=list(label=yLabel),
#                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
#                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
#                              x=list(at=atX),
#                              y=list(at=atY)
#                              ), 
#                  xlim=xLimits, #x axis limits
#                  ylim=yLimits, #y axis limits
                 panel = function(x, y){
                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
                 })
  return(plot)
}
@

>>>>

########################
# Creates a lattice plot that has the size of confidence intervals on the vertical axis and parameter
# values on the horizontal axis.
# At this point, this function is NOT a general-purpose function, as the number of permutations
# of model, parameter, energy type, and factor is too varied to be able to turn into a general-purpose 
# graph with little time investment at this point.
# This function makes a lattice plot with the following panels (in the arrangement shown)
#
# gammaCDeq   gammaCDex    gammaCDeu
# deltaCESeq  deltaCESex   deltaCESeu
# sigmaCESeq  sigmaCESex   sigmaCESeu
#
# Parameters and models (gamma for CDe and delta and sigma for CESe) are in rows and energyTypes (q, x, and u) 
# are in columns.
#
# textScaling: the amount by which you want to scale the text on the graph.
##
CIvsParamLattice <- function(textScaling=1.0, countryAbbrevScaling=1.0){
  # Set up plotting parameters that are common to both graphs.
  xTics <- c(0.0, 0.5, 1.0) #x axis tic locations
  yTics <- c(0.0, 1.0, 2.0) #y axis tic locations
  xLimits <- c(-0.2, 1.2) #x axis limits
  yLimits <- c(-0.4, 2.4) #y axis limits
  xLabels <- c("$\\gamma$", "$\\delta$", "$\\sigma$") #x axis labels
  yLabel <- "Width of 95\\% Confidence Interval"
  stripLabels <- c("CD with $q$", "CES with $q$", "CES with $q$",
                   "CD with $x$", "CES with $x$", "CES with $x$", 
                   "CD with $u$", "CES with $u$", "CES with $u$")
  stripBG <- "transparent"

  # Build a data.frame that contains coordinates for diagonal lines on the various graphs.
  # Columns are "param", "CI", and "factor" to match the column names later in this function.
  # Diagonal line for the gamma-CD-Q panel
  param <- c(0.0, 1.0)
  CI <- c(0.0, 2.0)
  factor <- c("gammaCDeQ", "gammaCDeQ")
  diagLineGammaCDeQDF <- data.frame(param, CI, factor)
  # Diagonal line for the gamma-CD-X panel
  factor <- c("gammaCDeX", "gammaCDeX")
  diagLineGammaCDeXDF <- data.frame(param, CI, factor)
  # Diagonal line for the gamma-CD-U panel
  factor <- c("gammaCDeU", "gammaCDeU")
  diagLineGammaCDeUDF <- data.frame(param, CI, factor)

  # Diagonal line for the delta-CES-Q panel  
  param <- c(1.0, 0.0)
  CI <- c(0.0, 2.0)
  factor <- c("deltaCESeQ", "deltaCESeQ")
  diagLineDeltaCESeQDF <- data.frame(param, CI, factor)
  # Diagonal line for the delta-CES-X panel  
  factor <- c("deltaCESeX", "deltaCESeX")
  diagLineDeltaCESeXDF <- data.frame(param, CI, factor)
  # Diagonal line for the delta-CES-U panel  
  factor <- c("deltaCESeU", "deltaCESeU")
  diagLineDeltaCESeUDF <- data.frame(param, CI, factor)

  # Diagonal line for the sigma-CES-Q panel  
  param <- c(0.0, 1.0)
  CI <- c(0.0, 2.0)
  factor <- c("sigmaCESeQ", "sigmaCESeQ")
  diagLineSigmaCESeQDF <- data.frame(param, CI, factor)
  # Diagonal line for the sigma-CES-X panel  
  factor <- c("sigmaCESeX", "sigmaCESeX")
  diagLineSigmaCESeXDF <- data.frame(param, CI, factor)
  # Diagonal line for the sigma-CES-U panel  
  factor <- c("sigmaCESeU", "sigmaCESeU")
  diagLineSigmaCESeUDF <- data.frame(param, CI, factor)

  # Now combine all data.frames in the correct order.
  diagLinesDF <- rbind(diagLineGammaCDeQDF, diagLineDeltaCESeQDF, diagLineSigmaCESeQDF,
                       diagLineGammaCDeXDF, diagLineDeltaCESeXDF, diagLineSigmaCESeXDF,
                       diagLineGammaCDeUDF, diagLineDeltaCESeUDF, diagLineSigmaCESeUDF)

  # Make an xyplot that contains the diagonal lines.
  diagLinesLattice <- xyplot(CI ~ param | factor, data=diagLinesDF,
                             scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                             alternating=FALSE, # eliminates left-right, top-bot alternating of axes
                             x=list(at=xTics),
                             y=list(at=yTics)
                             ), 
                             xlim=xLimits, 
                             ylim=yLimits, 
                             xlab=list(label=xLabels),
                             ylab=list(label=yLabel),
                             strip = strip.custom(factor.levels=stripLabels, # Set text for factor levels
                                                  bg=stripBG,
                                                  par.strip.text=list(cex=textScaling) # Scales text in the strip.
                                                  ),
                             as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                             )

  # Build a data.frame that has all the necessary data from the models.
  gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
  gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
  gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
  deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
  sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
  # Change the name of the first columns (the ones that contain the parameter of interest to us) to "param".
  # Doing this allows us to combine the individual data frames into one large data frame.
  colnames(gammaCDeqDF)[1]  <- "param"
  colnames(deltaCESeqDF)[1] <- "param"
  colnames(sigmaCESeqDF)[1] <- "param"
  colnames(gammaCDexDF)[1]  <- "param"
  colnames(deltaCESexDF)[1] <- "param"
  colnames(sigmaCESexDF)[1] <- "param"
  colnames(gammaCDeuDF)[1]  <- "param"
  colnames(deltaCESeuDF)[1] <- "param"
  colnames(sigmaCESeuDF)[1] <- "param"
  # Create one big data.frame with all of the data.
  data <- rbind(gammaCDeqDF, deltaCESeqDF, sigmaCESeqDF, 
                gammaCDexDF, deltaCESexDF, sigmaCESexDF,
                gammaCDeuDF, deltaCESeuDF, sigmaCESeuDF)
print(data)
  # Now make the graph.
  # Need to use the indices in the following code, because the column labels will be different for each type
  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
  # plot <-  xyplot(data$CI ~ data$sigma, ...)
  # would break if we, instead, wanted CESe with Q and plotting delta.
  # So, instead, we use the column indices to pick off the correct variables.
  # data[ , 1] contains the the parameter; 
  # data[ , 2] contains the CI width; 
  # data[ , 3] contains the descriptor for the type of graph it is.
  plot <- xyplot(CI ~ param | factor, data=data,
                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                             alternating=FALSE, # eliminates left-right, top-bot alternating of axes
                             x=list(at=xTics),
                             y=list(at=yTics)
                             ), 
                 xlim=xLimits, 
                 ylim=yLimits, 
                 xlab=list(label=xLabels),
                 ylab=list(label=yLabel),
                 # Set text for factor levels
                 strip = strip.custom(factor.levels=stripLabels, 
                                      bg=stripBG, # Sets background transparent to match the graph itself.
                                      par.strip.text=list(cex=textScaling) # Scales text in the strip.
                                      ),
                 as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                 panel = function(x, y){
                   # Picks up the 4th column containing the country abbreviations.
                   ltext(x=x, y=y, labels=data[ , 4], cex=countryAbbrevScaling) 
                 })
  #return(plot)
  return(diagLinesLattice)
}
@
